---
title: "week2"
author: "Ellen"
date: "2019/2/1"
output:
  ioslides_presentation: default
  beamer_presentation: default
  slidy_presentation: default
---

```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles()
my_map = leaflet()
my_map = addTiles(my_map)
my_map
```
```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet()  %>%
  addTiles()
my_map
```
```{r, eval=FALSE}
set.seed(2016-04-25)
df <- data.frame(lat=runif(20,min = 39.2, max = 39.3),
                 lng=runif(20, min = -76.6, max = -76.5))
df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers() 

```
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

